Full Title of Article\titlebreak This Title Has A Line Break

### 2021-09-12 Submission/Paper/Paper.tex
table 1 done

@@

>>>>

% table 1
\begin{table*}[hbtp]
\centering 
\floatconts
{tab:table1}
{\caption{Demographics of Data}} 
    {
        \begin{tabular}{lcccccc}
        \toprule
        \bfseries & \bfseries Mean Age (SD) & \bfseries Left Handed & \bfseries Right Handed & \bfseries \% Female & \bfseries Counts \\
        \midrule
        Healthy & 44.11 (15.46) & 7 & 46 & 54.7\% & 53 \\
        Healthy & 58.75 (7.51) & 5 & 69 & 20.3\% & 74 \\
        \bottomrule
        \end{tabular}
    }
\end{table*}

@@

The features were then normalized as follows:
\[f[i]' = \sum_\SUP{i=1}^9\frac{f[i] - avg(i)}{std(i)}\]
f[i]' represents the normalized equivalent of feature f[i] for features 1-9.

Additionally, we noticed there was a large class-imbalance present in our dataset, with 53 healthy and 105 PD patients. After performing experiments with our machine learning models, we discovered that this imbalance led to overfitting and undesirable accuracies, even after the assignation of higher weight to the healthy class. To cope with this, we truncated our original dataset by removing the 31 PD patients from the New HandPD dataset. This resulted in 127 patients, 53 healthy and 74 PD, which greatly boosted our results. Table \ref{tab:table1} shows our demographics for cohort of patients.
